# Missing values

All data are based on data provided by Law Enforcement in New York State. It’s already a summary integrating hate crimes happened in New York States from 2010 to 2018. In other words, the data here represent the numbers of hate crimes. If there is no hate crime of certain category, then the number will be 0.  

There is no null value in 'Hate_Crimes_by_County_and_Bias_Type__Beginning_2010.csv':

```{r, echo = TRUE}
dataset <- read.csv("Hate_Crimes_by_County_and_Bias_Type__Beginning_2010.csv")
any(is.na(dataset))
```

There is no null value in 'Hate_Crimes_data_Tidy.csv':

```{r, echo=TRUE}
dataset <- read.csv("Hate_Crimes_data_Tidy.csv")
any(is.na(dataset))
```

Also, it makes sense that the Law Enforcement Department already performed an initial data cleaning by filtering out the missing values. Though this no `NA` in datasets, we do found there two counties are not included, which are Wyoming County and Yates County. Given the fact that there are over 60 counties in New York State, we believe theses two missing counties can be ignored.